Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-21 cav2017/cav2017.tex
edited first approach

%-------------------------------
\subsection{Stability of closed-loop systems}
\label{sec:stability}
%-------------------------------

@@

1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to
compute a candidate solution $K$.

We compute a candidate $K$, with the required controller precision $\langle I_c,F_c\rangle$, that satisfies both the stability criteria detailed in 
section \todo{ref stability section}, and the safety specification in section \todo{ref for safety}.
The stability criteria are satisfied if the characteristic polynomial of $A_d - B_d * K_d$ meets Jury's criteria. This is 
independent of the initial states. 
In order to synthesise a controller for satisfaction of the safety specification, we unwind the transition system
$k$ steps, and pick a controller $K$ and an initial state such that the states at each step do not violate the safety criteria. 
The unwinding calculation includes the conversion from plant precision to the fixed point controller precision.

We assumes some
precision $\langle I_p,F_p\rangle$ for the plant, a $k$ and a sampling rate.  The
checks that these assumptions are sound are performed by subsequent
{\sc verify} stages.

@@

2. The first {\sc verify} stage, {\sc safety}, checks that the candidate
solution $K$ is safe for all possible initial states, i.e., does not reach an unsafe
state within $k$ steps.

The safety criteria here must be valid for all possible allowed initial states, and so we 
unwind the transition system $k$ steps, using the previously synthesised $K$, and check that
the state values at each step do not violate the safety bounds for any initial state.

@@

This check is potentially unsound because we consider the currently
assumed $\langle I_p,F_p\rangle$, $k$ and sampling rate.

>>>>

%-------------------------------
\subsection{Stability of closed-loop systems}
\label{ssec:stability}
%-------------------------------

@@

1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to
compute a candidate solution $K$
that satisfies both the stability criteria detailed in 
Sec.~\ref{ssec:stability} and the safety specification in Sec.~\ref{ssec:safety}.
%% The stability criteria are satisfied if the characteristic polynomial of $A_d - B_d * K_d$ meets Jury's criteria. This is 
%% independent of the initial states. 
Regarding the latter, we synthesise a safe controller by unwinding the transition system
$k$ steps and picking a controller $K$ and an initial state such that the states at each step do
not violate the safety criteria. This is sound if the current $k$ is below the
completeness threshold, which we assume to be true in the {\sc synthesize} phase.
We also assume some
precision $\langle I_p,F_p\rangle$ for the plant and a sampling rate.  The
checks that all these assumptions are sound are performed by subsequent
{\sc verify} stages.

@@

2. The first {\sc verify} stage, {\sc safety}, checks that the candidate
solution $K$ is safe for all possible initial states, i.e., does not reach an unsafe
state within $k$ steps where again we assume $k$ to be under the completeness threshold. 
%The safety criteria here must be valid for all possible allowed initial states, and so we
After unwinding the transition system corresponding to the previously synthesised controller
$k$ steps, we check that the safety specification holds for any initial state.

@@
